Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-09 presentacion_hiram/presentacion-tesis.tex
distribution

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz} 
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\begin{document}
	\author{Departamento de Investigacion en F\'isica \\
		Maestr\'ia en Ciencias (F\'isica)\\
		Hiram Ernesto Dami\'an}
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	%\date{}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}
\titlepage
\end{frame}

@@

\nologo{
\begin{frame}
\subsection{Higgs production mechanisms}
\frametitle{Higgs production mechanisms}
\begin{center}
\includegraphics[scale=0.4]{figures/pg.png}
\end{center}
\small{Different Higgs production mechanism, from the most likely to least likely}
\end{frame}
}
\begin{frame}
\frametitle{$tH$ production mechanisms}
\begin{center}
\begin{figure} 
\includegraphics[scale=0.4]{figures/tq.png} 
\caption*{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right)} 
\label{th}
\end{figure}
\end{center}
\end{frame}

@@

\begin{frame}
\subsection{Production cross section}
\frametitle{Cross section}
\begin{itemize}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\item Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
\end{itemize}
\end{frame}

@@

@@

\end{frame}
\begin{frame}
\subsection{BDT}
\frametitle{Boosted decision tree (BDT)}
\begin{itemize}
\item A decision tree takes a set of input features and splits input data recursively based on
those features.
Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
\item The BDT training is performed using several event variables for signal and background. 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{BDT Variables}
\small{
\begin{itemize}
\item A decision tree takes a set of input features and splits input data recursively based on
those features.
Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
\item The BDT training is performed using several event variables for signal and background. 
\end{itemize}
BDT Variables}
\tiny{
\begin{itemize}
\item	Trailing lepton $p_{t}$
\item 	Total charge of tight leptons
\item 	min $\Delta$R (lepton pairs)
\item 	$\Delta\phi$ between highest $p_t$ lepton pair
\item 	Number of jets with |$\eta$| < 2.4
\item	Number of non b-tagged jets with |$\eta$| > 1.0
\item	Maximum |$\eta$| for jets
\item	$\Delta\eta$ (most forward light jet, closest lepton)
\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{itemize} }
\end{frame}

@@

>>>>

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz} 
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
\begin{document}
	\author{Departamento de Investigacion en F\'isica \\
		Maestr\'ia en Ciencias (F\'isica)\\
		Hiram Ernesto Dami\'an}
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	%\date{}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}
\titlepage
\end{frame}

@@

\nologo{
\begin{frame}
\subsection{Higgs production mechanisms and decays}
\frametitle{Higgs production mechanisms}
\begin{center}
\includegraphics[scale=0.4]{figures/pg.png}
\end{center}
\small{Different Higgs production mechanism, from the most likely to least likely}
\end{frame}
}
\begin{frame}
\frametitle{$tH$ production mechanisms}
\begin{center}
\begin{figure} 
\includegraphics[scale=0.4]{figures/tq.png} 
\caption*{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right)} 
\label{th}
\end{figure}
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\item Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Backgrounds}
\begin{itemize}
	\item Backgrounds are considered information in the data that is not the signal. 
	\item Backgrounds share certain characteristics of the signal.
	\item Backgrounds are a big factor in the statistical of the signal.
\end{itemize}
\end{frame}

@@

\begin{frame}
\subsection{BDT}
\frametitle{BDT}
\small{
\begin{itemize}
\item A decision tree takes a set of input features and splits input data recursively based on
those features.
Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
\item The BDT training is performed using several event variables for signal and background. 
\end{itemize}
BDT Variables}
\tiny{
\begin{itemize}
\item	Trailing lepton $p_{t}$
\item 	Total charge of tight leptons
\item 	min $\Delta$R (lepton pairs)
\item 	$\Delta\phi$ between highest $p_t$ lepton pair
\item 	Number of jets with |$\eta$| < 2.4
\item	Number of non b-tagged jets with |$\eta$| > 1.0
\item	Maximum |$\eta$| for jets
\item	$\Delta\eta$ (most forward light jet, closest lepton)
\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{itemize} }
\end{frame}

\nologo{
	\begin{frame}
	\Fontvi
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta} &
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}\\ 
			{Distribution of selected events as a function of $|\eta|$ of the jet with largest value of $|\eta|$} & {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } \\
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\
			{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events as function of $|\eta|$ between a forward jet and a b-tagged jet } \\
		\end{tabular}
	\end{center}
\end{frame}
}

\nologo{
	\begin{frame}

		\Fontvi
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\ 
			{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {Distribution of jet events for $|\eta|$>1} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}&
			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-sch}\\
			{Distribution of events of $|\Delta\phi|$ between the higher pt pair of leptons } & {Distribution of events of the sum of same sign leptons charge.} \\
		\end{tabular}
	\end{center}
\end{frame}
}

@@

\begin{frame}
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/compare_variables}
	\caption*{Signal and background kinematic distributions}
\end{figure}
\end{frame}
